Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-17 WSSSPE2_report/WSSSPE2_review.tex
Front matter and Section 1:  minor changes.

\todo{update this section with intro to full report - currently just intro for pre-workshop stuff}

link to live notes -
\url{tinyurl.com/q6ew45v}%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing}

>>>>

\todo{update this section with intro to full report - currently just intro for pre-workshop stuff. Link to live notes -
\url{tinyurl.com/q6ew45v}}
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
